### 2025-07-24 README.Rmd
update ref to published version

Ryan, G.E., Tierney, N., Golding, N., and Weiss, D.J (2025). [traveltime: an R package to calculate travel time across a landscape from user-specified locations](https://doi.org/10.31223/X56M74){target="_blank"}. **EarthArXiv** 10.31223/X56M74

>>>>

Ryan, G.E., Tierney, N., Golding, N., and Weiss, D.J (2025). [traveltime: an R package to calculate travel time across a landscape from user-specified locations](https://doi.org/10.12688/gatesopenres.16356.1){target="_blank"}. Gates Open Research 9:50
